### 2019-02-03 results.tex
mz - hyphenation
minor

\begin{table}[t]
\centering
%\scriptsize
%\resizebox{\columnwidth}{!}{
\begin{tabular}{|l|l|} \hline
\textbf{Application}& \textbf{Description}\\
\hline
Prophet& Time series decomposition and prediction\\ 
\hline
Multi-Regression& Multiple linear regression/prediction of time series\\
\hline
XGBoost& Regression and classification by gradient boosting\\
\hline
SVC & Classification based on support vector machine\\
\hline
NN& Classification by layered artificial neural network\\
\hline
\end{tabular}
%}
\caption{Machine learning applications used as benchmarks
to evaluate Seneca. 
%paper submission is blind (so such references must be omitted so as not to reveal our identities):
%Code base is available at project repository~\cite{ref:seneca}.
\label{tab:bmarks}}
%\vspace{-0.2in}
\end{table}

@@

\begin{table}[t]
\centering
\scriptsize
%\resizebox{\columnwidth}{!}{
\begin{tabular}{|l|l|l|} 
\hline
\textbf{Hyperparameter}& \textbf{Default} & \textbf{Tuning options}\\
\hline
grow & linear & [linear, logistic] \\
\hline
changepoint prior scale & 0.05 & [0.05, 0.5] \\
\hline
holidays prior scale & 10 & [1, 5, 10] \\
\hline
seasonality prior scale & 0.5 & [0.1, 0.5] \\
\hline
fourier order & 10 & [5, 10, 15, 20] \\
\hline
seasonality mode & additive & [additive, multiplicative] \\
\hline
interval width & 0.8 & [0.5, 0.8] \\
\hline
\end{tabular}
%}
\caption{The hyperparameters that Seneca considers for Prophet. 
The default value and tuning options are listed. 
\label{tab:prophet_para}}
\vspace{-0.2in}
\end{table}

@@

\begin{table}[t]
\centering
\scriptsize
\input{hparams-svc-tab}
\caption{The hyperparameters that Seneca considers for SVC. 
The default value and tuning options are listed. 
\label{tab:svc_para}}
\vspace{-0.2in}
\end{table}

@@

\subsection{Benchmark Applications and Training/Testing  Datasets}
The machine learning applications that we use to evaluate Seneca 
are shown in Table~\ref{tab:bmarks}, each with 
a brief description.
Prophet~\cite{ref:prophet} is a time series analysis library built and maintained by Facebook and the open-source community. The input dataset is a time series of view counts
%logorithm
of Payton Manning's wikipedia page from Dec. 10th, 2007 to Jan. 20th, 2016. 
The dataset exhibits both seasonality and a holiday effect (e.g. around the super bowl games). 
We use the first 6 years as the training set and the last 2 years as the testing set.
We use a cross-validation horizon (sliding window) of 1-year, 
and a period (sliding pace) 
of 180 days.  As such, Seneca performs three cross-validations for each 2-year testing range.

@@

In the results that follow, we evaluate \textit{default} parameteterizations (that come with 
the application or that are defined by the application developer) for each application.  
The default parameters and tuning options for Prophet are listed in the table~\ref{tab:prophet_para}. For every cross validation, the application computes mean square error (MSE) as $\frac{1}{n}\sum_{i=1}^{n}(Y_i - \hat{Y_i})$, where $\hat{Y_i}$ is the ground truth, $Y_i$ is model prediction and n is the number of data points. Then the application returns the average MSE of all cross validation. Based on the model trained by default parameter setting, this average MSE metric is 0.284.

Multi-Regression is a regression application 
from an IoT project~\cite{iot-cpu} that was developed by the authors
to predict outdoor temperature from the processor 
temperature of single board computers (SBCs).  
The technique uses multiple linear regression models computed from time
series of processor temperature measurements,
to predict outdoor microclimate temperatures without using a temperature sensor.
%(e.g. for use in 
%precision agriculture applications such as irrigation control and frost protection).
The training dataset consists of eight input time series (one per SBC, each containing 
5-minute measurements) from April 5th, 2018 to Dec. 10th, 2018.

@@

XGBoost~\cite{ref:xgboost-web} is an open source framework for gradient boosting, which 
performs both regression and classification. We consider it a regression application and
a classification application in this evaluation.  
The hyperparmeters and their defaults that Seneca uses in this study are listed in Table~\ref{tab:xgboost_para}. A definition for each hyperparameter can be found at~\cite{ref:xgboostparams}.
%xgboostparams: https://xgboost.readthedocs.io/en/latest/python/python_api.html#module-xgboost.sklearn
Support vector classification (SVC)~\cite{ref:svc} is a classification algorithm 
based on support vector machine and implemented by libsvm~\cite{ref:libsvm} library.
The hyperparmeters and their defaults that Seneca uses for SVC in this study are listed in Table~\ref{tab:svc_para}. A definition for each hyperparameter can be found at~\cite{ref:svcparams}.
%xvcparams: https://scikit-learn.org/stable/modules/generated/sklearn.svm.SVC.html
Neural network (NN)~\cite{ref:neural_network} is a machine learning framework that learns 
and make decisions from patterns in an input dataset. For this application, 
we use a feedforward multilayer perceptron model~\cite{ref:feedforward_nn} 
for the classification task.
The hyperparmeters and their defaults that Seneca uses for Neural Network in this study are listed in Table~\ref{tab:nn_para}. A definition for each hyperparameter can be found at~\cite{ref:nnparams}.
%nn: https://scikit-learn.org/stable/modules/generated/sklearn.neural_network.MLPClassifier.html

@@

These applications compute classification accuracy score
as $\frac{1}{n}\sum_{i=1}^{n}1(Y_i = \hat{Y_i})$, where $Y_i$ is the
prediction class, $Y_i$ is the true class, $n$ is the number of samples, and 1(x)
is the indicator function. XGBoost also computes MSE for its regression task
on the same datasets. The dataset has been filtered to remove correlated
features (those with an absolute value of the Pearson correlation coefficient
greater than 0.8). The dataset has also been balanced by downsampling one
target whose number greatly exceeds other ones. The resulting dataset contains
33926 rows (individual fruit) distributed evenly to 5 targets and each row has
18 features.

@@

%using the three regression applications: 
%Prophet, Multi-Regression, and XGBoost (regression task). 
Table~\ref{tab:mse} shows the effect of Seneca on the quality of the
regressions generated by Prophet, Multi-regression, and XGBoost (when used as
a regression algorithm). The first row indicates the number of
different hyperparameter settings Senica considered.  Rows 3 through 5 show
the MSE generated by the default hyperparameter settings, the best (lowest
MSE) Seneca was able to find, and the worst (largest MSE) that Seneca tested
for each regression algorithm and dataset.

@@

We next analyze the monetary costs incurred by Seneca.  To do so, we
use Seneca to find the hyperparameterization that optimizes application output
quality (lowest MSE for regression, highest accuracy for classification).
For each hyperparameteriyation that Seneca evaluates, it incurs a
cost. Furthermore, the amount of memory used by Seneca during memory
tuning also influeces overall cost.

Thus, instead of trying out all possible settings,  we compare two
Seneca execution configurations.  In the first 
we configure each lambda function to
use the maximum amount of memory allowed by AWS Lambda (3008 MB) for all
executions.
Second, we
employ Seneca's memory optimization which automatically detects and configures
the amount of memory needed by each function.  This optimization requires
Seneca to ``probe'' to determine the best memory size to use.  The
cost of these probes
(denoted ``Optimizer Cost'') must be taken intio account as well.
%Because memory impacts both
%cost and execution time (total latency of Seneca hyperparameter tuning), we
%present empirically evaluate both in this subsection.  
Note that XGBoost's performance profile is identical when used for regression
or classification so we include its measurements only once in the following
analysis.
%For each, we only
%include XGBoost once since its performance profile is the same regardless of
%whether we are using regression or classification.

@@

% \textcolor{blue}{It would be good here in the Seneca case to also run the applications in the minumum amount of memory discovered by Seneca (ie if we were to run Seneca ahead of time, taking the max memory used by any of the functions per application) -- to show what Seneca is missing.  this assumes you are doing the memory optimization WHILE you are doing the tuning -- if you are not, you can leave this out, but we need to remind the reader at this point how the memory optimization is done by Seneca (we should do this in this paragraph, either way).}

@@

%\textcolor{red}{Add analysis here on what the columns are showing -- discuss
%any anomalies (ie why is prophet optimization cost more than the others; why
%mult-regression difference is greater than the others). provide a summary for
%that states the average difference between each pair of bars across
%applications.}

>>>>

\begin{table}[t]
\centering
%\scriptsize
%\resizebox{\columnwidth}{!}{
\begin{tabular}{|l|l|} \hline
\textbf{Application}& \textbf{Description}\\
\hline
Prophet& Time series decomposition and prediction\\ 
\hline
Multi-Regression& Multiple linear regression/prediction of time series\\
\hline
XGBoost& Regression and classification by gradient boosting\\
\hline
SVC & Classification based on support vector machine\\
\hline
NN& Classification by layered artificial neural network\\
\hline
\end{tabular}
%}
\caption{Machine learning applications used as benchmarks
to evaluate Seneca. 
%paper submission is blind (so such references must be omitted so as not to reveal our identities):
%Code base is available at project repository~\cite{ref:seneca}.
\label{tab:bmarks}}
\vspace{-0.2in}
\end{table}

@@

\begin{table}[t]
\centering
\scriptsize
%\resizebox{\columnwidth}{!}{
\begin{tabular}{|l|l|l|} 
\hline
\textbf{Hyperparameter}& \textbf{Default} & \textbf{Tuning options}\\
\hline
grow & linear & [linear, logistic] \\
\hline
changepoint prior scale & 0.05 & [0.05, 0.5] \\
\hline
holidays prior scale & 10 & [1, 5, 10] \\
\hline
seasonality prior scale & 0.5 & [0.1, 0.5] \\
\hline
fourier order & 10 & [5, 10, 15, 20] \\
\hline
seasonality mode & additive & [additive, multiplicative] \\
\hline
interval width & 0.8 & [0.5, 0.8] \\
\hline
\end{tabular}
%}
\caption{The hyperparameters that Seneca considers for Prophet. 
The default value and tuning options are listed. 
\label{tab:prophet_para}}
%\vspace{-0.2in}
\end{table}

@@

\begin{table}[t]
\centering
\scriptsize
\input{hparams-svc-tab}
\caption{The hyperparameters that Seneca considers for SVC. 
The default value and tuning options are listed. 
\label{tab:svc_para}}
%\vspace{-0.2in}
\end{table}

@@

\subsection{Benchmark Applications and Training/Testing  Datasets}
The machine learning applications that we use to evaluate Seneca 
are shown in Table~\ref{tab:bmarks}, each with 
a brief description.
Prophet~\cite{ref:prophet} is a time series analysis library built and maintained by Facebook and the open-source community. The input dataset is a time series of view counts
%logorithm
of Peyton Manning's Wikipedia page from Dec. 10th, 2007 to Jan. 20th, 2016. 
The dataset exhibits both seasonality and a holiday effect (e.g. around the super bowl games). 
We use the first 6 years as the training set and the last 2 years as the testing set.
We use a cross-validation horizon (sliding window) of 1-year, 
and a period (sliding pace) 
of 180 days.  As such, Seneca performs three cross-validations for each 2-year testing range.

@@

In the results that follow, we evaluate \textit{default} parameterizations (that come with 
the application or that are defined by the application developer) for each application.  
The default parameters and tuning options for Prophet are listed in the table~\ref{tab:prophet_para}. For every cross validation, the application computes mean square error (MSE) as $\frac{1}{n}\sum_{i=1}^{n}(Y_i - \hat{Y_i})$, where $\hat{Y_i}$ is the ground truth, $Y_i$ is model prediction and n is the number of data points. Then the application returns the average MSE of all cross validation. Based on the model trained by default parameter setting, this average MSE metric is 0.284.

Multi-Regression is a regression application 
from an IoT project~\cite{iot-cpu} that was developed (and extended
from linear regression described in the citation, 
to multiple linear regression) by the authors.
The application predicts outdoor temperature from the processor 
temperature of single board computers (SBCs).  
The technique uses multiple linear regression models computed from time
series of processor temperature measurements,
to predict outdoor microclimate temperatures without using a temperature sensor.
%(e.g. for use in 
%precision agriculture applications such as irrigation control and frost protection).
The training dataset consists of eight input time series (one per SBC, each containing 
5-minute measurements) from April 5th, 2018 to Dec. 10th, 2018.

@@

XGBoost~\cite{ref:xgboost-web} is an open source framework for gradient boosting, which 
performs both regression and classification. We consider it a regression application and
a classification application in this evaluation.  
The hyperparmeters and their defaults that Seneca uses in this study are listed in Table~\ref{tab:xgboost_para}. A definition for each hyperparameter can be found at~\cite{ref:xgboostparams}.
%xgboostparams: https://xgboost.readthedocs.io/en/latest/python/python_api.html#module-xgboost.sklearn
Support vector classification (SVC)~\cite{ref:svc} is a classification algorithm 
based on support vector machine and implemented by libsvm~\cite{ref:libsvm} library.
The hyperparmeters and their defaults that Seneca uses for SVC in this study are listed in Table~\ref{tab:svc_para}. A definition for each hyperparameter can be found at~\cite{ref:svcparams}.
%xvcparams: https://scikit-learn.org/stable/modules/generated/sklearn.svm.SVC.html
Neural network (NN)~\cite{ref:neural_network} is a machine learning framework that learns 
and make decisions from patterns in an input dataset. For this application, 
we use a feed-forward multi-layer perceptron model~\cite{ref:feedforward_nn} 
for the classification task.
The hyperparmeters and their defaults that Seneca uses for Neural Network in this study are listed in Table~\ref{tab:nn_para}. A definition for each hyperparameter can be found at~\cite{ref:nnparams}.
%nn: https://scikit-learn.org/stable/modules/generated/sklearn.neural_network.MLPClassifier.html

@@

These applications compute classification accuracy score
as $\frac{1}{n}\sum_{i=1}^{n}1(Y_i = \hat{Y_i})$, where $Y_i$ is the
prediction class, $Y_i$ is the true class, $n$ is the number of samples, and 1(x)
is the indicator function. XGBoost also computes MSE for its regression task
on the same datasets. The dataset has been filtered to remove correlated
features (those with an absolute value of the Pearson correlation coefficient
greater than 0.8). The dataset has also been balanced by down-sampling one
target whose number greatly exceeds other ones. The resulting dataset contains
33926 rows (individual fruit) distributed evenly to 5 targets and each row has
18 features.

@@

%using the three regression applications: 
%Prophet, Multi-Regression, and XGBoost (regression task). 
Table~\ref{tab:mse} shows the effect of Seneca on the quality of the
regressions generated by Prophet, Multi-regression, and XGBoost (when used as
a regression algorithm). The first row indicates the number of
different hyperparameter settings Seneca considered.  Rows 3 through 5 show
the MSE generated by the default hyperparameter settings, the best (lowest
MSE) Seneca was able to find, and the worst (largest MSE) that Seneca tested
for each regression algorithm and dataset.

@@

We next analyze the monetary costs incurred by Seneca.  To do so, we
use Seneca to find the hyperparameterization that optimizes application output
quality (lowest MSE for regression, highest accuracy for classification).
For each hyperparameterization that Seneca evaluates, it incurs a
cost. Furthermore, the amount of memory used by Seneca during memory
tuning also influences overall cost.

Thus, instead of trying out all possible settings,  we compare two
Seneca execution configurations.  In the first 
we configure each lambda function to
use the maximum amount of memory allowed by AWS Lambda (3008 MB) for all
executions.
Second, we
employ Seneca's memory optimization which automatically detects and configures
the amount of memory needed by each function.  This optimization requires
Seneca to ``probe'' to determine the best memory size to use.  The
cost of these probes
(denoted ``Optimizer Cost'') must be taken into account as well.
%Because memory impacts both
%cost and execution time (total latency of Seneca hyperparameter tuning), we
%present empirically evaluate both in this subsection.  
Note that XGBoost's performance profile is identical when used for regression
or classification so we include its measurements only once in the following
analysis.
%For each, we only
%include XGBoost once since its performance profile is the same regardless of
%whether we are using regression or classification.

@@

% \textcolor{blue}{It would be good here in the Seneca case to also run the applications in the minimum amount of memory discovered by Seneca (i.e., if we were to run Seneca ahead of time, taking the max memory used by any of the functions per application) -- to show what Seneca is missing.  this assumes you are doing the memory optimization WHILE you are doing the tuning -- if you are not, you can leave this out, but we need to remind the reader at this point how the memory optimization is done by Seneca (we should do this in this paragraph, either way).}

@@

%\textcolor{red}{Add analysis here on what the columns are showing -- discuss
%any anomalies (i.e., why is prophet optimization cost more than the others; why
%mult-regression difference is greater than the others). provide a summary for
%that states the average difference between each pair of bars across
%applications.}
